---
title: "hw7"
author: "Emma Chung"
date: "2025-04-04"
output: pdf_document
---

GtHub link: 

```{r}
library(tidyverse)
library(ggplot2)
library(MatchIt)
```

# Problem 1: Armfold

```{r}
armfold <- read_csv("armfold.csv")
```

## A.

```{r}
# number of male and female in the dataset
table(armfold$Sex)
```

```{r}
# proportion of males with left on top
male_left <- armfold %>% 
  filter(Sex == "Male") %>% 
  filter(LonR_fold == "1")
male_left_prop <- count(male_left) / 106
male_left_prop
```

```{r}
# proportion of females with left on top
female_left <- armfold %>% 
  filter(Sex == "Female") %>% 
  filter(LonR_fold == "1")
female_left_prop <- count(female_left) / 111
female_left_prop
```

## B.

```{r}
prop_diff <- male_left_prop - female_left_prop
prop_diff
```

## C.

```{r}
# standard error for difference in proportion
se <- sqrt((male_left_prop * (1 - male_left_prop))/106 + (female_left_prop * (1 - female_left_prop))/111)
conf_low_95 <- prop_diff - 1.96 * se
conf_high_95 <- prop_diff + 1.96 * se
```

The confidence interval is between `r conf_low_95` and `r conf_high_95`. The formula for difference in proportion is square root of p1(1 - p1)/N1 + p2(1 - p2)/N2. Values I pluggged in the formula are p1 = 0.08490566, p2 = 0.08108108, N1 = 106, and N2 = 111. The z value I use here is +-1.96.

## D. 
If we were to determine the difference between probability of a man has his left hand on top and probability of a woman has her left hand on top, then we would expect that if we repeat the test many times and calculate the difference in probability, 95% of time the difference of probability will be between `r conf_low_95` and `r conf_high_95`.

## E,
The standard error I calculated above present how spread out the confidence interval is.

## F. 
Sampling distribution refers to the repeated process of resample from our bigger sample dataset, from each time sampling, what will be the difference between 

## G.
normal distribution

## H.
There is not significant difference in sex in terms of armfolding, but it can be a hidden confounder that contribute to the different hands on top.

## I.
Yes. The confidence interval is calculated using the difference in proportion and standard error. Accross different groups, there will likely be different standard error or difference in proportion that leads to a different confidence interval. It should be true that the collection of all those interval should not vary too much.

# Problem 2: Get out the vote

```{r}
turnout <- read_csv("turnout.csv")
```

## A.

```{r}
# proportion of those receiving a GOTV call who voted in 1998
gotv <- turnout %>% 
  filter(GOTV_call == 1)
gotv_1998 <- turnout %>% 
  filter(GOTV_call == 1) %>% 
  filter(voted1998 == 1)
gotv_1998_prop <- count(gotv_1998)/count(gotv)

# gotv_1998_prop = 0.64778
```

```{r}
# proportion of those not receiving a GOTV call who voted in 1998
nogotv_1998 <- turnout %>% 
  filter(GOTV_call == 0) %>% 
  filter(voted1998 == 1)
nogotv_1998_prop <- count(nogotv_1998)/count(turnout)
nogotv_1998_prop
```
```{r}
# voter turnout rates in 1998 between those who received a call and those who did not
prop_diff_gotv <- gotv_1998_prop - nogotv_1998_prop
prop_diff_gotv
```

```{r}
# 95% confidence level in diiference in gotv_1998 and nogotv_1998
se_gotv <- sqrt((gotv_1998_prop ** 2)/count(gotv_1998) + ((nogotv_1998_prop) ** 2)/count(nogotv_1998))
conf_low_95_gotv <- prop_diff_gotv - 1.96 * se_gotv
conf_high_95_gotv <- prop_diff_gotv + 1.96 * se_gotv
```

The 95% confidence interval will be between `r conf_low_95_gotv` and `r conf_high_95_gotv`.

## B.

```{r}
# voted 1996 and received a GOTV call
gotv_1996 <- turnout %>% 
  filter(GOTV_call == 1) %>% 
  filter(voted1996 == 1)
gotv_1996_prop <- count(gotv_1998)/count(turnout)
# gotv_1996_prop = 0.01478

nogotv_1996 <- turnout %>% 
  filter(GOTV_call == 1) %>% 
  filter(voted1996 == 0)
nogotv_1996_prop <- count(nogotv_1996)/count(turnout)
# nogotv_1996_prop - 0.00656

prop_diff_1996 <- gotv_1996_prop - nogotv_1996_prop
# prop_diff_1996 = 0.0082

se_1996 <- sqrt((gotv_1996_prop * (1 - gotv_1996_prop)/ count(gotv_1996)) + nogotv_1996_prop * (1 - nogotv_1996_prop)/count(nogotv_1996))
# se_1996 = 0.0132
conf_low_1996 <- prop_diff_1996 - 1.96 * se_1996
conf_high_1996 <- prop_diff_1996 + 1.96 * se_1996

# graphs or set of summary stats
turnout_b <- turnout %>% 
  mutate(GOTV_tf = ifelse(GOTV_call == 1, "No", "Yes")) %>% 
  filter(voted1996 == "1")
ggplot(turnout_b, aes(x = GOTV_tf)) + geom_bar(stat = "count") + labs(title = "Number of People who Voted in 1996 and did or didn't Received a GOTV Call", x = "Received a Call or not")
```

The 95% confidence interval of difference in proportion of people who voted in 1996 and received a GOTV call and people who voted in 1996 but did not receive a call is between `r conf_low_1996` and `r conf_high_1996`.

```{r}
# age and received a call?
gotv_age <- turnout %>% 
  filter(GOTV_call == 1) 
gotv_age_mean <- mean(gotv_age$AGE)
gotv_age_sd <- sd(gotv_age$AGE)
# gotv_age_mean = 58.301

nogotv_age <- turnout %>% 
  filter(GOTV_call == 0)
nogotv_age_mean  <- mean(nogotv_age$AGE)
nogotv_age_sd <- sd(nogotv_age$AGE)
# nogotv_age_mean = 49.425

se_age <- sqrt(gotv_age_sd ** 2/count(gotv_age) + nogotv_age_sd ** 2/count(nogotv_age))
conf_low_age <- (gotv_age_mean - nogotv_age_mean) - 1.96 * se_age
conf_high_age <- (gotv_age_mean - nogotv_age_mean) + 1.96 * se_age

# plot
turnout_b2 <- turnout %>% 
  select(GOTV_call, AGE) %>% 
  mutate(gotv_tf = ifelse(GOTV_call == 1, "Yes", "No"))
ggplot(turnout_b2, aes(x = gotv_tf, y = AGE)) + geom_boxplot()
```

The 95% confidence interval of difference in mean of people's age who received a GOTV call and people who did not receive a call is between `r conf_low_age` and `r conf_high_age`.

```{r}
# majority party member?
gotv_majorpty <- turnout %>% 
  filter(GOTV_call == 1) %>% 
  filter(MAJORPTY == 1)
gotv_majorpty_prop <- count(gotv_majorpty)/count(turnout)
# gotv_majorpty_prop = 0.0183

nogotv_majorpty <- turnout %>% 
  filter(GOTV_call == 0) %>% 
  filter(MAJORPTY == 1)
nogotv_majorpty_prop <- count(nogotv_majorpty)/count(turnout)
# nogotv_majorpty_prop = 0.00452

se_majorpty = sqrt((gotv_majorpty_prop * (1 - gotv_majorpty_prop)/count(gotv_majorpty)) + (nogotv_majorpty_prop * (1 - nogotv_majorpty_prop)/count(nogotv_majorpty)))
conf_low_majorpty <- (gotv_majorpty_prop - nogotv_majorpty_prop) - 1.96 * se_majorpty
conf_high_majorpty <- (gotv_majorpty_prop - nogotv_majorpty_prop) + 1.96 * se_majorpty

# plot
turnout_b2 <- turnout %>% 
  mutate(GOTV_tf = ifelse(GOTV_call == 1, "Yes", "No")) %>% 
  filter(voted1996 == "1")
ggplot(turnout_b, aes(x = GOTV_tf)) + geom_bar(stat = "count") + labs(title = "Number of People who Voted in 1996 and did or didn't Received a GOTV Call", x = "Received a Call or not")
```

The 95% confidence interval of difference in proportion of people who are majorpty and received a GOTV call and people who are majorpty but did not receive a call is between `r conf_low_majorpty` and `r conf_high_majorpty`.

# C.

```{r}
# matching
call_match = matchit(GOTV_call ~ voted1996 + AGE + MAJORPTY, data = turnout, ratio=5)

# extract matching data
call_match = match.data(call_match)

# proportion of those receiving a GOTV call who voted in 1998
gotv_1998_match <- call_match %>% 
  filter(GOTV_call == 1) %>% 
  filter(voted1998 == 1)

gotv_1998_match_prop = count(gotv_1998_match)/count(call_match)
# gotv_1998_match_prop = 0.108

# sample proportion of those not receiving a GOTV call who voted in 1998
nogotv_1998_match <- call_match %>% 
  filter(GOTV_call == 0) %>% 
  filter(voted1998 == 1)

nogotv_1998_match_prop = count(nogotv_1998_match)/count(call_match)
# nogotv_1998_match_prop = 0.474

se_match = sqrt(gotv_1998_match_prop * (1 - gotv_1998_match_prop)/count(gotv_1998_match) + nogotv_1998_match_prop * (1 - nogotv_1998_match_prop)/count(nogotv_1998_match))
# se_match = 0.0309

conf_low_match = (gotv_1998_match_prop - nogotv_1998_match_prop) - 1.96 * se_match
conf_high_match = (gotv_1998_match_prop - nogotv_1998_match_prop) + 1.96 * se_match
```

The 95% confidence interval from matched dataset of difference in proportion of people who voted in 1998 and received a GOTV call and people who did not vote in 1998 but did not receive a call is between `r conf_low_match` and `r conf_high_match`.

I would conclude that receiving a GOTV will reduce the probability a person vote in the 1998 election, which is really weird because the intention of the phone call is to urge people go out and vote.