---
title: "hw8"
author: "Emma Chung (hc33293)"
date: "2025-04-12"
output:
  pdf_document: default
  html_document: default
---

GitHub:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2)
library(tidyverse)
library(mosaic)
```

# Problem 1: regression warm up

```{r}
creatinine <- read_csv("creatinine.csv")
```

## A
What creatinine clearance rate should we expect for a 55-year-old? Explain briefly how you determine this.

```{r, echo = FALSE}
# linear regression model
clearance_rate = lm(creatclear ~ age, data = creatinine)
coef(clearance_rate)
```

```{r, echo = FALSE}
# 55-year-old in the model
clearance_rate_55 <- 147.8129158 - 0.6198159 * 55
```

From our regression model, which has intercept of 147.8129158 and slope of -0.6198159, we can calculate the expected creatinine clearance rate of a 55-year-old is `r round(clearance_rate_55, 4)`.

## B
How does creatinine clearance rate change with age?
In the regression model I built for this question, creatinine clearance rate change with age is -0.6198 ml/minute per year. 

## C
Whose creatinine clearance rate is healthier (higher) for their age: a 40-year-old with a rate of 135, or a 60-year-old with a rate of 112?

```{r, echo = FALSE}
clearance_rate_40 <- 147.8129158 - 0.6198159 * 40
clearance_rate_60 <- 147.8129158 - 0.6198159 * 60

df <- tibble(
  age = c("40", "60"),
  expected_rate = c(clearance_rate_40, clearance_rate_60),
  real_rate = c("135", "112"),
  variation = c(round((135 - clearance_rate_40)/clearance_rate_40, 4), round((112 - clearance_rate_60)/clearance_rate_60, 4))
)
df
```

The 40-year-old is healthier in terms of creatinine clearance rate. While both subjects has higher creatinine clearance rate than the expected rate calculated by the regression model, the 40-year-old is 9.74% higher and the 60-year-old is 1.24% higher.


\newpage
# Problem 2: Modeling disease growth

```{r}
covid <- read_csv("covid.csv")
```
## 1
An estimated growth rate and doubling time for Italy, with 95% bootstrapped confidence intervals for each.

```{r, echo = FALSE}
italy <- covid %>% 
  filter(country == "Italy")
```

```{r, echo = FALSE}
# bootstrap 95% conf interval
boot_italy = do(10000)*lm(log(deaths) ~ days_since_first_death, data = resample(italy))
confint(boot_italy, level = 0.95)
```
The estimated growth rate for Italy is 0.183, with 95% bootstrapped confidence interval is between 0.159 and 0.208.

```{r, echo = FALSE}
#italy_rate = 1.019
italy_rate_low = 0.159
italy_rate_high = 0.208

# doubling time
# italy_time = round(1/italy_rate * log(2), 1)
italy_time = log(2)/0.183

# bootstrap 95% conf interval
italy_time_low = round(1/italy_rate_low* log(2), 1)
italy_time_high = round(1/italy_rate_high * log(2), 1)
```

The estimated doubling time for Italy is 3.8 days, with 95% bootstrapped confidence interval is between 3.3 and 4.4 days.

## 2
An estimate growth rate and doubling time for Spain, with 95% bootstrapped confidence intervals for each

```{r, echo = FALSE}
spain <- covid %>% 
  filter(country == "Spain")
```

```{r, echo = FALSE}
# growth rate
boot_spain = do(10000)*lm(log(deaths) ~ days_since_first_death, data = resample(spain))
confint(boot_spain, level = 0.95)
```
The estimated growth rate for Spain is 0.276, with 95% bootstrapped confidence interval is between 0.235 and 0.316.

```{r, echo = FALSE}
# doubling time
spain_rate_low = 0.235
spain_rate_high = 0.316

spain_time = round(1/0.276 * log(2), 1)
spain_time

# bootstrap 95% conf interval
spain_time_low = round(1/spain_rate_low* log(2), 1)
spain_time_high = round(1/spain_rate_high * log(2), 1)
```

The estimated doubling time for Spain is 2.5 days, with 95% bootstrapped confidence interval is between 2.2 and 2.9 days.

## 3
```{r, echo = FALSE}
ggplot(covid, aes(x = days_since_first_death, y = deaths, color = country)) + geom_line() +
  labs(title = "Deaths in Italy and Spain since the First Death Report Day", 
       x = "Day since the First Death", y = "Death Count")
```

\newpage
# Problem 3: price elasticity of demand

```{r, echo = FALSE, message = FALSE, warning = FALSE}
milk <- read_csv("milk.csv")
```

```{r, echo = FALSE}
boot_milk = do(10000)*lm(log10(sales) ~ log10(price), data=resample(milk))
confint(boot_milk, level = 0.95)
```

The estimated price elasticity of demand for milk is -1.619. The 95% confidence interval is between - 1.773 and -1.455. Since this is.a power-law model, the given equation will only be linear when both sides take log. Consequently, the slope of the linear regression model is the elasticity of demand.
